Score-based tests of measurement invariance: Use in practice

### 2013-10-28 frontiers/frontiers.Rnw
change simulation 2 according to Achim's 2-round comments.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@287 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\subsection{Results}
Results of
primary interest are conditions where the unmodeled loading violates
measurement invariance.  A subset of results is displayed in Figure~\ref{fig:sim21res}.  One can generally observe
that tests of the first loading and unique variance exhibited high
``power,'' which is actually a high Type I error rate here.  This Type
I error also demonstrated when testing all loadings and all unique
variances, as shown in the appendix.  Tests
associated with the factor 
covariance (not shown) did not demonstrate this error, however. In
terms of specific 
statistic performance, $\max \mathit{LM}_o$ and $\mathit{WDM}_o$ 
demonstrated higher Type I error than $\mathit{LM}_{uo}$ in each panel,
especially with increasing levels.  This is likely because the unmodeled
loading's non-invariance was monotonic with $V$; if it were not monotonic, we
would expect $\mathit{LM}_{uo}$ to have higher Type I error.

@@

In summary, the proposed test statistics appear robust to unmodeled loading parameters, so long
as the umodeled parameter does not violate measurement invariance.  If the unmodeled parameter 
dose violate measurement invariance, however, then the tests assign this violation to other 
parameters that do not violate measurement invariance.  The impacted parameters include the error
variance and other loadings associated with the manifest variable
associated with the unmodeled 
loading.  Thus, as for other tests of measurement invariance, it is important to study the extent to
which the hypothesized model includes all parameters of importance.

@@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is the unmodeled
loading. Panel labels denote the parameter(s) 
being tested and the number of levels of the ordinal variable $m$.}
\label{fig:sim21res}
<<sim21res, fig=TRUE, height=7, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra" & 
		 pars %in% c("Loading1", "Error1") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude (Unmodeled Loading)",
       ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(1, 3)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@

>>>>

\subsection{Results}
Results of
primary interest are conditions where the unmodeled loading violates
measurement invariance.  A subset of results is displayed in Figure~\ref{fig:sim21res}.  One can generally observe
that tests of the first loading and unique variance exhibited high
``power,'' which is actually a high Type I error rate here.  This Type
I error also demonstrated when testing all loadings and all unique
variances, as shown in the appendix.  Tests
associated with the factor 
covariance \seeme{delete the ''not shown''} did not demonstrate this error, however.  In
terms of specific 
statistic performance, $\max \mathit{LM}_o$ and $\mathit{WDM}_o$ 
demonstrated higher Type I error than $\mathit{LM}_{uo}$ in each panel,
especially with increasing levels.  This is likely because the unmodeled
loading's non-invariance was monotonic with $V$; if it were not monotonic, we
would expect $\mathit{LM}_{uo}$ to have higher Type I error.

@@

In summary, the proposed test statistics appear robust to unmodeled loading parameters, so long
as the umodeled parameter does not violate measurement invariance.  If the unmodeled parameter 
dose violate measurement invariance, however, the test could detect there existing measurement invariance in the model but assign this violation to other 
parameters that do not violate measurement invariance.  \seeme{add the point that the tests could detect measurement invariance}.  The impacted parameters include the error
variance and other loadings associated with the manifest variable
associated with the unmodeled 
loading.  Thus, as for other tests of measurement invariance, it is important to study the extent to
which the hypothesized model includes all parameters of importance.  The tests are model-based and could not inform the researcher model misspecification. \seeme{The last sentence.}

@@

\begin{figure}
\caption{Simulated power curves for $\max \mathit{LM}_o$, $\mathit{WDM}_o$, and $\mathit{LM}_{uo}$ across three levels of the ordinal variable $m$ and measurement invariance 
violations of 0--4 standard errors (scaled by $\sqrt{n}$). The
parameter violating measurement invariance is the unmodeled
loading. Panel labels denote the parameter(s) 
being tested and the number of levels of the ordinal variable $m$.}
\label{fig:sim21res}
<<sim21res, fig=TRUE, height=9, width=9, echo=FALSE>>=
trellis.par.set(theme = canonical.theme(color = FALSE))
mykey <- simpleKey(levels(sim2$test), points = TRUE, lines = TRUE)
xyplot(power ~ diff | nlevels + pars, group = ~ test, data = sim2,
       subset = (parms == "extra" & 
		 pars %in% c("Loading1", "Covariance", "Error1") & diff %% 0.5 == 0),
       type = "b", xlab = "Violation Magnitude (Unmodeled Loading)",
       ylab = "Power", key = mykey, as.table = TRUE,
       strip = function(..., which.given, factor.levels){
	   if(which.given == 2){
	       strip.default(which.given, factor.levels = parlabs[c(1, 2, 3)], ...)
	   } else {
	       strip.default(which.given, factor.levels = factor.levels, ...)
	   }
       })
@
